Test parsing of Proff.no table (Kreftforeningen)

### 2022-07-07 Test parsing of Proff table.Rmd
Visualisations.

read_proff2("Links/Kors.html", "2001", "2020") |> 
  arrange(desc(year))
```

>>>>

Kors <- read_proff2("Links/Kors.html", "2001", "2020") |> 
  arrange(desc(year))
```

### Visualisations
```{r}
Kors |> 
  filter(REGNSKAPSPERIODE == "Årsresultat") |> 
  ggplot(aes(year, value)) +
  geom_col()

Kors |> 
  filter(REGNSKAPSPERIODE == "SUM EGENKAPITAL OG GJELD") |> 
  ggplot(aes(year, value)) +
  geom_col()
```
